---
title: "Common Deliverable"
output: 
 flexdashboard::flex_dashboard:
    orientation: rows
    runtime: shiny
    vertical_layout: fill
runtime: shiny
---

```{r Load Packages, include=FALSE}

library(tm)
library(flexdashboard)
library(shiny)
library(quanteda)
library(RYandexTranslate)
library(stm)
library(wordcloud)
library(htmlwidgets)
library(stmBrowser)
library(devtools)
library(jsonlite)
library(SnowballC)
library(ggplot2)
library(cluster)
library(fpc)
library(xlsx)
library(plotly)
library(likert)
library(grid)
library(rJava)
devtools::install_github("timelyportfolio/stmBrowser@htmlwidget") # This needs to be installed once


```

```{r Load Moldova Dataset, include=FALSE, echo=TRUE}
##  SETUP
# N.B: Knitr CANNOT DEAL with the "setwd" function. Even if the WD is already correct, if it reads "setwd" it will reset it to some random temp directory. Set your working directory before you knit, and it should be fine.
##  Load Data

dataset <- "moldova"
save("dataset", file = "dataset.txt")

# This needs to be set for "Data Cleaning.R" to work. (Choose from "kyrgyzstan", "moldova", "unicef", "serbia", "tajikistan", "yemen")
```

```{r Translation Switch, include=FALSE, echo=TRUE}
## Switchboard

switch_t <- 0 # Translation
switch_c <- 1 # Corpus
save(list = c("switch_c","switch_t"), file = "switches.RData")

if (!exists("clean",where = .GlobalEnv))
  {source("Data Cleaning.R", echo = TRUE)}
```

```{r Descriptive Stats, include=FALSE, echo = TRUE}
##  Descriptive Statistics 

# Currently works for Moldova, and will for Kyrgyzstan when we have more characters for Yandex.

source("Descriptive Stat Builder.R", echo = TRUE) # ERROR: Errorin eval(expr, envir, enclos) : object 'DQ1.Age' not found

search <- search()
if (!is.na(match("clean", search))) {detach(clean)}
if (!is.na(match("data", search))) {detach(data)}
if (is.na(match("clean", search))) {attach(clean)}
```

```{r Readfeeling Function (Loads all datasets)}
# Functions
# Alternatively:
# source("myreadfeeling.R") # Read and clear data bases
readfeeling <- function(fname,myLevs=3){
  require(xlsx)
  # myLevs: Number of levels: 3 or 5 (leave original #levels unaltered?)
  # Default: myLevs <- 3
  Lev3 <- c("negative","neutral","positive")
  clev3 <- c(-1,0,1)
  Lev5 <- c("strongly negative","negative","neutral","positive","strongly positive")
  clev5 <- c(-1,-0.5,0,0.5,1)
  #print(paste("Data",fname))
  data <- read.xlsx2(fname,1) # Works and fast (NA become void or 0)
  N <- dim(data)[1]
  #print(paste(" #records=",N,"\n"))
  # Different countries have different field names for the feeling, all starting with Q1.Feeling
  # Force naming them Q1.Feeling
  # First find the column matching "Q1."
  ind <- pmatch("Q1",names(data))
  # Then force renaming that column "Q1.Feeling"
  names(data)[ind] <- "Q1.Feeling"
  # Remove dots from filed names because some countries have and some not
  # "." has to be written as a special character "\\."
  names(data) <- gsub("\\.","",names(data))
  data$feeling <- data$Q1Feeling
  data$feeling[data$feeling==""] <- NA
  feeling_Nlev <- length(levels(data$feeling)) # Numer of levels of feeling
  # Some missing data generate a new level. Discard them
  if ("" %in% levels(data$feeling))
    feeling_Nlev <- feeling_Nlev-1
  # Some countries have data only on 3 levels (strongly is lacking)
  # For uniformity revert feeling to 3 levels
  if (myLevs == 3) {
    if (feeling_Nlev==5) {
      # Some countries have 5 levels of feeling (include "strongly")
      # Convert "strongly negative" to "negative" and "strongly positive" to "positive"
      data$feeling[data$feeling=="strongly negative"] <- "negative"
      data$feeling[data$feeling=="strongly positive"] <- "positive"
      # Drop former "strongly" levels
      data$feeling <- droplevels(data$feeling)
    }
    # Set Nlev to 3
    feeling_Nlev <- 3
    Lev <- Lev3
    clev <- clev3
  }
  if (myLevs == 5) {
    if (feeling_Nlev==3) {
      levels(data$feeling) <- Lev5
      # Some countries have only 3 levels of feeling ("negative","neutral","positive")
      # Convert "negative" to "strongly negative" and "positive" to "strongly positive"
      data$feeling[data$feeling=="negative"] <- "strongly negative"
      data$feeling[data$feeling=="positive"] <- "strongly positive"
    }
    # Set Nlev to 5
    feeling_Nlev <- 5
    Lev <- Lev5
    clev <- clev5
  }
  
  # Order the levels of feeling in the right order (otherwise ordered alphabetically)
  data$feeling <- ordered(data$feeling, levels = Lev)
  data$feeling_num <- rep(NA,N)
  for (nlev in 1:feeling_Nlev)
    data$feeling_num[data$feeling==levels(data$feeling)[nlev]] <- clev[nlev]
  # feeling_avg <- mean(feeling_num,na.rm=TRUE)
  # dum (the date and hour) is integer as coming from read.xlsx2
  dum <- data$XEntryDate
  # treated as character and then as numeric
  data$timedate_num <- as.numeric(as.character(dum))
  # Convert to day-time format
  # from p. 31 of the xlsx pdf guide https://cran.r-project.org/web/packages/xlsx/xlsx.pdf
  data$timedate <- as.POSIXct((data$timedate_num-25569)*86400, tz="GMT", origin="1970-01-01")
  
  return(data)
}

```

```{r Chiara Country Object}
# Initial parameters

# Alternatively:
# source("myparameters.R")
Ncountry <- 5
Country <- array(list(), Ncountry)
# Country 1: Yemen
Country[[1]] <- list(country = "Yemen", countrycode = "YEM", fname = "foiyemen2015_Standard_english.xlsx",
                     latmin = 12, latmax = 19, lonmin = 42, lonmax = 55)
# Country 2: Kirghizistan
Country[[2]] <- list(country = "Kirghizistan", countrycode = "KGZ", fname = "foikyrg2015_Standard.xlsx",
                     latmin = 39, latmax = 43.5, lonmin = 72, lonmax = 80.5)
# Country 3: Moldova
Country[[3]] <- list(country = "Moldova", countrycode = "MDA", fname = "foimoldova2015_Standard.xlsx",
                     latmin = 28, latmax = 48.5, lonmin = 26.5, lonmax = 30.5)
# Country 4: Tajikistan
Country[[4]] <- list(country = "Tajikistan", countrycode = "TJK", fname = "tajikistan2015_Standard.xlsx",
                     latmin = 36.5, latmax = 41.5, lonmin = 67, lonmax = 75.5)
# Country 4: Serbia
Country[[5]] <- list(country = "Serbia", countrycode = "SRB", fname = "foiserbia2015_Standard.xlsx",
                     latmin = 42, latmax = 46.5, lonmin = 18.5, lonmax = 23)

# Read and clean data bases (possibly to split in two parts)

# Alternatively:
# source("myread.R") # uses myreadfeeling
#timedate_num_all <- numeric(0)
#Country_all <- character(0)
#feeling_all <- numeric(0)

data <- array(list(),Ncountry)
for (ncountry in 1:Ncountry){
  data[[ncountry]] <- readfeeling(Country[[ncountry]]$fname)
  
  if (ncountry == 1) {
    # Convert to character because concatenating factors looses the factor property
    feeling_all <- as.character(data[[ncountry]]$feeling)
    timedate_num_all <- data[[ncountry]]$timedate_num
    Country_all <- rep(Country[[ncountry]]$country,length(data[[ncountry]]$feeling))
  } else {
    feeling_all <- c(feeling_all,as.character(data[[ncountry]]$feeling))
    timedate_num_all <- c(timedate_num_all,data[[ncountry]]$timedate_num)
    Country_all <- c(Country_all,rep(Country[[ncountry]]$country,length(data[[ncountry]]$feeling)))
  }
}
```

Topics {.sidebar}
=============================================================================

```{r}
selectInput("Country", label = "Country",
            choices = c("All","Yemen","Kirghizistan","Moldova","Tajikistan","Serbia"), selected = "Yemen")
sliderInput("Cut_days", label = "Window length (days)",
            min = 3, max = 30, value = 7, step = 1)

# selectInput("list_of_topics", label = "Choose a topic:",
#            choices = c("education", "health", "corruption", "migration"))

# selectInput("gender", label = "Choose gender:", choices = (c("All", "Female", "Male")))

# selectizeInput("age", label = "Choose age groups:", choices = (c("Under 17", "17-29", "30-44", "45-60", "Over 60")), multiple = TRUE)
# 
# selectizeInput("education", label = "Choose education level:", choices = c("No formal education", "Primary education", "Secondary education", "technical/vocational education", "university degree", "master and/or phd"), multiple = TRUE)
# 
# selectizeInput("employment", label = "Choose employment status:", choices = c("student", "salaried professional", "self employed/entrepreneur", "volunteer", "unemployed", "out of the workforce", "retired", "other"), multiple = TRUE)
# 
# selectizeInput("where", label = "Choose area:", choices = c("Urban", "Rural"), multiple = TRUE)
# 
# selectizeInput("levelofincome", label = "Choose income level:", choices = c("less than others in my community", "more or less the same", "more than others in the community"), multiple = TRUE)
```

Search a Key Word in Context

```{r}
textInput("KWICInput", label = NULL, value = "job", placeholder = "e.g. job")
```

World Map {data-orientation=columns}
=====================================  

Column {data-width=650}
-------------------------------------

### Map of Average Feeling (Positive/Negative/Neutral) Reflected in MicroNarratives Collected

```{r Feeling Map}
renderPlotly({

mycountries <- character(Ncountry)
mycodes <- character(Ncountry)
avg_feeling <- numeric(Ncountry)
minlat=100
maxlat=-100
minlon=200
maxlon=-200
for (ncountry in 1:Ncountry){
  mycountries[ncountry] <- Country[[ncountry]]$country
  mycodes[ncountry] <- Country[[ncountry]]$countrycode
  avg_feeling[ncountry] <- mean(data[[ncountry]]$feeling_num,na.rm=TRUE)
  minlat <- min(minlat,Country[[ncountry]]$latmin)
  minlon <- min(minlon,Country[[ncountry]]$lonmin)
  maxlat <- max(maxlat,Country[[ncountry]]$latmax)
  maxlon <- max(maxlon,Country[[ncountry]]$lonmax)
}

df <- data.frame(country=mycountries,
                 code=mycodes,
                 feeling=avg_feeling)

df$hover <- with(df,paste(country, " (",code,"). Average feeling: ",format(feeling,digits=2),sep=""))
# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = TRUE,
  projection = list(type = 'Mercator'),
  showland = TRUE,
  landcolor = toRGB("grey83"),
  #subunitcolor = toRGB("white"),
  countrycolor = toRGB("white"),
  showlakes = TRUE,
  lakecolor = toRGB("white"),
  #showsubunits = TRUE,
  showcountries = TRUE,
  resolution = 50,
  countrywidth = 0.5,
  subunitwidth = 0.5,
  lonaxis=list(showgrid=TRUE,range=c(minlon,maxlon)),
  lataxis=list(showgrid=TRUE,range=c(minlat,maxlat)),
  showlakes=TRUE,
  lakecolor = toRGB("white")
  #  showcountry=TRUE
)

#print(
  plot_ly(df,
        z = feeling,
        locations = code,
        type = 'choropleth',
        color = feeling,
        colors = c("red","green"), # 'Blues',
        marker = list(line = l),
        colorbar = list(title = 'Feeling'),
        hoverinfo = "text", #  "a",..., "text", "name" with a "+" OR "all" or "none".
        text=hover
) %>%
  layout(title = '',
         geo = g) %>%
  add_trace(type="scattergeo",
          locations = code, text = country, mode="text")
#)
  
})
```

Column
-------------------------------------

### Countries data

```{r}
overview <- read.table("countries.csv", header = TRUE, sep = ";", dec = ",")
knitr::kable(overview)
```

### Time trend of stories
```{r}

renderPlot({

  Cut_days <- reactCut_days() # equivalently input$Cut_days

    feeling_all <- factor(feeling_all)
    mindate <- min(timedate_num_all)
    maxdate <- max(timedate_num_all)
    Ncut <- ceiling((maxdate-mindate)/Cut_days)
    print(paste("#Bins for the whole time span:",Ncut,"(bin width in days:",Cut_days,")"))
    
    # Cut time interval into Ncut bins
    # timedate_num_cut includes the reference bin of each data
    # Increase the number of digits to 10 because default 5 digits only gives days
    timedate_num_cut <- cut(timedate_num_all,Ncut,dig.lab=10)
    # The levels contain the boundaries of the bins
    labs <- levels(timedate_num_cut)
    # Convert from character to numeric removing parentheses (from the official documentation of cut)
    # dum is a matrix with left and right boundaries as columns
    dum <- cbind(as.numeric( sub("\\((.+),.*", "\\1", labs) ),
                 as.numeric( sub("[^,]*,([^]]*)\\]", "\\1", labs) ))
    # Compute the bin centers
    timedate_num_cutcenter <- rowMeans(dum)
    timedate_cutcenters <- as.POSIXct((timedate_num_cutcenter-25569)*86400, tz="GMT", origin="1970-01-01")
    
    timedate_cut <- timedate_num_cut
    for (nlev in 1:length(levels(timedate_cut))){
      dum <- as.character(timedate_cutcenters[nlev])
      # Discard time and take only the day
      dum <- substr(dum,1,10)
      # Convert data. Take account that year is with 4 digits (20...)
      dum <- as.Date(dum,"20%y-%m-%d")
      # Convert date to Month day 
      levels(timedate_cut)[nlev] <- format(dum,"%b %d")
    }
    
    # Plot of percentage of answers over time by countries
    dflik <- data.frame(Country_all)
    names(dflik) <- "All countries"
    lik <- likert(dflik,grouping=timedate_cut)
    plot(lik,TYPE="bar",include.histogram = TRUE,panel.arrange = "v",
         plot.percents=FALSE,include.center=FALSE,centered=FALSE,
         plot.percent.low = FALSE, plot.percent.high = FALSE, plot.percent.neutral = FALSE,
         color=rainbow(Ncountry),
         label.completed = "Stories", label.missing = "NA",
         group.order=rev(levels(timedate_cut)),
         xlab="# Stories")

})
```

Feeling (Positive/Negative) Over Time {data-orientation=rows}
=====================================   

Row
-------------------------------------

### Scatter plot

```{r Cut Days}

# Define input parameters to be exchanged
#
# Cut days is the window (in days) for analyzing time series

reactCut_days <- reactive(input$Cut_days)
reactncountry <- reactive({
  switch(input$Country,"All"={ncountry<-0}, "Yemen"={ncountry<-1},
         "Kirghizistan"={ncountry<-2}, "Moldova"={ncountry<-3},
         "Tajikistan"={ncountry<-4},"Serbia"={ncountry<-5})
})  
```

```{r Feeling Jitter Plot}
renderPlot({
  ncountry <- reactncountry()
  Cut_days <- reactCut_days() # equivalently input$Cut_days
  if (ncountry>0){ # Single countries
    
    feeling_values <- as.numeric(levels(as.factor(data[[ncountry]]$feeling_num)))
    
    # Convert to data.frame because of ggplot
    df <- data.frame(timedate=data[[ncountry]]$timedate,feeling=data[[ncountry]]$feeling)
    # Add some jitter to the feeling to avoid overlap of dots
    p <- ggplot(na.omit(df),aes(x=timedate,y=feeling))
    p <- p + geom_point(position=position_jitter(width=0,height=0.075))
    p <- p + ggtitle(Country[[ncountry]]$country)
    p <- p + labs(x="Time",y="Feeling")
    print(p) # Mandatory if run with source, otherwise it does not print
  }
})
```  

### Mean Trend

```{r Feeling Mean Trend}
renderPlot({
  
  ncountry <- reactncountry()
  Cut_days <- reactCut_days() # equivalently input$Cut_days
  
  if (ncountry>0){ # Single countries
    
    
    # Duplicated because not saved from the previous chunk
    feeling_values <- as.numeric(levels(as.factor(data[[ncountry]]$feeling_num)))
    
    #
    # Time series of average feeling
    #
    mindate <- min(data[[ncountry]]$timedate_num)
    maxdate <- max(data[[ncountry]]$timedate_num)
    Ncut <- ceiling((maxdate-mindate)/Cut_days)
    print(paste("#Bins for the time span:",Ncut,"(bin width in days:",Cut_days,")"))
    
    # Cut time interval into Ncut bins
    # timedate_num_cut includes the reference bin of each data
    # Increase the number of digits to 10 because default 5 digits only gives days
    timedate_num_cut <- cut(data[[ncountry]]$timedate_num,Ncut,dig.lab=10)
    # The levels contain the boundaries of the bins
    labs <- levels(timedate_num_cut)
    # Convert from character to numeric removing parentheses (from the official documentation of cut)
    # dum is a matrix with left and right boundaries as columns
    dum <- cbind(as.numeric( sub("\\((.+),.*", "\\1", labs) ),
                 as.numeric( sub("[^,]*,([^]]*)\\]", "\\1", labs) ))
    # Compute the bin centers
    timedate_num_cutcenter <- rowMeans(dum)
    timedate_cutcenters <- as.POSIXct((timedate_num_cutcenter-25569)*86400, tz="GMT", origin="1970-01-01")
    
    timedate_cut <- timedate_num_cut
    for (nlev in 1:length(levels(timedate_cut))){
      dum <- as.character(timedate_cutcenters[nlev])
      # Discard time and take only the day
      dum <- substr(dum,1,10)
      # Convert data. Take account that year is with 4 digits (20...)
      dum <- as.Date(dum,"20%y-%m-%d")
      # Convert date to Month day (add Year?)
      levels(timedate_cut)[nlev] <- format(dum,"%b %d")
    }
    
    tab <- table(data[[ncountry]]$feeling,timedate_num_cut)
    
    # Compute Weighted mean and standard deviation inside bins
    feeling_mean <- rep(0,Ncut)
    feeling_std <- rep(0,Ncut)
    for (ncut in 1:Ncut){
      feeling_mean[ncut] <- weighted.mean(feeling_values,tab[,ncut])
      feeling_std[ncut] <- sqrt(sum(tab[,ncut] * (feeling_values - feeling_mean[ncut])^2)/(sum(tab[,ncut])*(sum(tab[,ncut])-1)))
    }
    
    p <- qplot(timedate_cutcenters,feeling_mean)
    p <- p + geom_errorbar(aes(x=timedate_cutcenters, ymin=feeling_mean-feeling_std, ymax=feeling_mean+feeling_std))
    p <- p + ggtitle(Country[[ncountry]]$country)
    p <- p + labs(x="Time",y="Feeling")
    print(p) # Mandatory if run with source, otherwise it does not print
    
    # Copy data[[ncountry]] into datadum because error in lm otherwise
    datadum <- data[[ncountry]]
    # Test by ANOVA whether the means in the bins are all equal
    fit <- lm(formula = datadum$feeling_num ~ timedate_num_cut)
    res <- anova(fit)
    
    print(paste("p-value of Test equal means (ANOVA):",res$`Pr(>F)`[1]))
    
  } # End of if (ncountry>0)
  
}) # End of renderPlot()

``` 

Row
-------------------------------------

### Likert Plot

```{r Feeling Likert Plot}
renderPlot({
  
  ncountry <- reactncountry()
  Cut_days <- reactCut_days() # equivalently input$Cut_days
  
  if (ncountry>0){ # Single countries
    
    # Duplicated because not saved from the previous chunk
    mindate <- min(data[[ncountry]]$timedate_num)
    maxdate <- max(data[[ncountry]]$timedate_num)
    Ncut <- ceiling((maxdate-mindate)/Cut_days)
    print(paste("#Bins for the time span:",Ncut,"(bin width in days:",Cut_days,")"))
    
    # Cut time interval into Ncut bins
    # timedate_num_cut includes the reference bin of each data
    # Increase the number of digits to 10 because default 5 digits only gives days
    timedate_num_cut <- cut(data[[ncountry]]$timedate_num,Ncut,dig.lab=10)
    # The levels contain the boundaries of the bins
    labs <- levels(timedate_num_cut)
    # Convert from character to numeric removing parentheses (from the official documentation of cut)
    # dum is a matrix with left and right boundaries as columns
    dum <- cbind(as.numeric( sub("\\((.+),.*", "\\1", labs) ),
                 as.numeric( sub("[^,]*,([^]]*)\\]", "\\1", labs) ))
    # Compute the bin centers
    timedate_num_cutcenter <- rowMeans(dum)
    timedate_cutcenters <- as.POSIXct((timedate_num_cutcenter-25569)*86400, tz="GMT", origin="1970-01-01")
    
    timedate_cut <- timedate_num_cut
    for (nlev in 1:length(levels(timedate_cut))){
      dum <- as.character(timedate_cutcenters[nlev])
      # Discard time and take only the day
      dum <- substr(dum,1,10)
      # Convert data. Take account that year is with 4 digits (20...)
      dum <- as.Date(dum,"20%y-%m-%d")
      # Convert date to Month day (add Year?)
      levels(timedate_cut)[nlev] <- format(dum,"%b %d")
    }
    # End duplication
    
    # Likert plots
    
    dflik <- data.frame(data[[ncountry]]$feeling)
    # Change name of the variable because printed in the plot
    names(dflik) <- Country[[ncountry]]$country
    lik <- likert(dflik,grouping=timedate_cut)
    # Using include.histrogram = TRUE is bugging with ggtitle(title) and ordering of the histogram
    # Note that + ggtitle(Country[[ncountry]]$country) does not work when including histogram
    plot(lik,TYPE="bar",include.histogram = TRUE,panel.arrange = "v",group.order=rev(levels(timedate_cut)),
         label.completed = "Stories", label.missing = "NA",
         xlab="# Stories")
    
    
    
  } else { # All countries 
    feeling_all <- factor(feeling_all)
    mindate <- min(timedate_num_all)
    maxdate <- max(timedate_num_all)
    Ncut <- ceiling((maxdate-mindate)/Cut_days)
    print(paste("#Bins for the whole time span:",Ncut,"(bin width in days:",Cut_days,")"))
    
    # Cut time interval into Ncut bins
    # timedate_num_cut includes the reference bin of each data
    # Increase the number of digits to 10 because default 5 digits only gives days
    timedate_num_cut <- cut(timedate_num_all,Ncut,dig.lab=10)
    # The levels contain the boundaries of the bins
    labs <- levels(timedate_num_cut)
    # Convert from character to numeric removing parentheses (from the official documentation of cut)
    # dum is a matrix with left and right boundaries as columns
    dum <- cbind(as.numeric( sub("\\((.+),.*", "\\1", labs) ),
                 as.numeric( sub("[^,]*,([^]]*)\\]", "\\1", labs) ))
    # Compute the bin centers
    timedate_num_cutcenter <- rowMeans(dum)
    timedate_cutcenters <- as.POSIXct((timedate_num_cutcenter-25569)*86400, tz="GMT", origin="1970-01-01")
    
    timedate_cut <- timedate_num_cut
    for (nlev in 1:length(levels(timedate_cut))){
      dum <- as.character(timedate_cutcenters[nlev])
      # Discard time and take only the day
      dum <- substr(dum,1,10)
      # Convert data. Take account that year is with 4 digits (20...)
      dum <- as.Date(dum,"20%y-%m-%d")
      # Convert date to Month day 
      levels(timedate_cut)[nlev] <- format(dum,"%b %d")
    }
    
    # Plot of percentage of answers over time by countries
    dflik <- data.frame(Country_all)
    names(dflik) <- "All countries"
    lik <- likert(dflik,grouping=timedate_cut)
    plot(lik,TYPE="bar",include.histogram = TRUE,panel.arrange = "v",
         plot.percents=FALSE,include.center=FALSE,centered=FALSE,
         plot.percent.low = FALSE, plot.percent.high = FALSE, plot.percent.neutral = FALSE,
         color=rainbow(Ncountry),
         label.completed = "Stories", label.missing = "NA",
         group.order=rev(levels(timedate_cut)),
         xlab="# Stories")
  }
}) # End of renderPlot

```




Topic overview {data-navmenu="Kyrgyzstan"} 
==============================================================================


Text analysis {data-navmenu="Kyrgyzstan"}
==============================================================================

Stories {data-navmenu="Kyrgyzstan"}
==============================================================================

Key Words in Context {data-navmenu="Kyrgyzstan"}
==============================================================================


Topic overview {data-navmenu="Moldova"}
==============================================================================

Row {data-height=650}
------------------------------------------------------------------

```{r, include=FALSE}
moldova <- read.csv("Moldova_1.csv")

moldovatext <- Corpus(VectorSource(moldova$"Your.experience"))
moldovatext <- tm_map(moldovatext, removePunctuation)

for(j in seq(moldovatext))   
{   
  moldovatext[[j]] <- gsub("/", " ", moldovatext[[j]])   
  moldovatext[[j]] <- gsub("@", " ", moldovatext[[j]])   
  moldovatext[[j]] <- gsub("\\|", " ", moldovatext[[j]]) 
}  

moldovatext <- tm_map(moldovatext, removeNumbers)  
moldovatext <- tm_map(moldovatext, tolower)
moldovatext <- tm_map(moldovatext, removeWords, stopwords("english")) 

# library(SnowballC)   
moldovatext <- tm_map(moldovatext, stemDocument) 
moldovatext <- tm_map(moldovatext, stripWhitespace) 

moldovatext <- tm_map(moldovatext, PlainTextDocument) 

## Stage the data

dtm <- DocumentTermMatrix(moldovatext)   
dtm   

tdm <- TermDocumentMatrix(moldovatext)   
tdm   

freq <- colSums(as.matrix(dtm))   
length(freq)  

ord <- order(freq) 

freq[head(ord)] 
freq[tail(ord)] 

head(table(freq), 20)  
tail(table(freq), 20)  

findFreqTerms(dtm, lowfreq=20)

wf <- data.frame(word=names(freq), freq=freq)   
head(wf)  

```

### Wordclouds

```{r}
#(wordcloud) 
wordcloud(names(freq), freq, min.freq=20)
```


### Word frequency
```{r}
# library(ggplot2)   
p <- ggplot(subset(wf, freq>20), aes(word, freq))    
p <- p + geom_bar(stat="identity")   
p <- p + theme(axis.text.x=element_text(angle=45, hjust=1))   
p
```



Text analysis {data-navmenu="Moldova"}
==============================================================================
```{r, include=FALSE}
temp<-textProcessor(documents=clean$texts,metadata=clean)
meta<-temp$meta
vocab<-temp$vocab
docs<-temp$documents
out <- prepDocuments(docs, vocab, meta)
docs<-out$documents
vocab<-out$vocab
meta <-out$meta
meta$EntryDate <- as.Date(meta$EntryDate)
meta$DQ2.Gender <- as.factor(meta$DQ2.Gender)
meta$DQ3.Education <- as.factor(meta$DQ3.Education)
meta$DQ1.Age <- as.factor(meta$DQ1.Age)

```


```{r, include=FALSE}
#Run STM. We can include more metadata if we want
names(clean)
ferdigB <- stm(docs, vocab, 8, prevalence  =~ EntryDate + DQ1.Age + DQ3.Education + DQ2.Gender + Q7.Score, data = meta)
```


### Cluster analysis

```{r, include = FALSE}
dtmss <- removeSparseTerms(dtm, 0.95) # This makes a matrix that is only 15% empty space, maximum.   
inspect(dtmss) 

# library(cluster)   
d <- dist(t(dtmss), method="euclidian")   
fit <- hclust(d=d, method="ward")   
fit   

plot(fit, hang=-1)  

plot.new()
plot(fit, hang=-1)
groups <- cutree(fit, k=5)   # "k=" defines the number of clusters you are using   
rect.hclust(fit, k=5, border="red")

# library(fpc)   
d <- dist(t(dtmss), method="euclidian")   
kfit <- kmeans(d, 2)   

```

```{r}
clusplot(as.matrix(d), kfit$cluster, color=T, shade=T, labels=2, lines=0) 
```

Labels STM {data-navmenu="Moldova"}
===================================== 
```{r}
labelTopics(ferdigB, topics=NULL, n = 7, frexweight = 0.5)
```

Clouds STM {data-navmenu="Moldova"}
==================================================
```{r, echo=FALSE}
cloud(ferdigB, topic=1, type=c("model", "documents"),
      documents, thresh=.9, max.words=100)
text(x=0.5, y=1, "Topic 1")
cloud(ferdigB, topic=2, type=c("model", "documents"),
      documents, thresh=.9, max.words=100)
text(x=0.5, y=1, "Topic 2")
cloud(ferdigB, topic=3, type=c("model", "documents"),
      documents, thresh=.9, max.words=100)
text(x=0.5, y=1, "Topic 3")
cloud(ferdigB, topic=4, type=c("model", "documents"),
      documents, thresh=.9, max.words=100)
text(x=0.5, y=1, "Topic 4")
cloud(ferdigB, topic=5, type=c("model", "documents"),
      documents, thresh=.9, max.words=100)
text(x=0.5, y=1, "Topic 5")
cloud(ferdigB, topic=6, type=c("model", "documents"),
      documents, thresh=.9, max.words=100)
text(x=0.5, y=1, "Topic 6")
cloud(ferdigB, topic=7, type=c("model", "documents"),
      documents, thresh=.9, max.words=100)
text(x=0.5, y=1, "Topic 7")
cloud(ferdigB, topic=8, type=c("model", "documents"),
      documents, thresh=.9, max.words=100)
text(x=0.5, y=1, "Topic 8")
```

Explore STM {data-navmenu="Moldova"}
===================================== 
```{r STM Browser, echo=FALSE}
stmBrowser_widget(ferdigB, data=meta, c("EntryDate","DQ1.Age","DQ3.Education", "DQ2.Gender", "Q7.Score"),text="texts", labeltype='frex') 
```


Stories {data-navmenu="Moldova"}
==============================================================================

Key Words in Context {data-navmenu="Moldova"}
==============================================================================

### Key Words in Context

```{r Moldova KWIC}
renderPrint({
  options(width = 200)
  print(as.data.frame(kwic(corpus, input$KWICInput)[,3:5]), row.names = F)
})
```


Topic overview {data-navmenu="Serbia"}
==============================================================================


Text analysis {data-navmenu="Serbia"}
==============================================================================

Stories {data-navmenu="Serbia"}
==============================================================================

Key Words in Context {data-navmenu="Serbia"}
==============================================================================


Topic overview {data-navmenu="Tajikistan"}
==============================================================================

Text analysis {data-navmenu="Tajikistan"}
==============================================================================

Stories {data-navmenu="Tajikistan"}
==============================================================================

Key Words in Context {data-navmenu="Tajikistan"}
==============================================================================


Topic overview {data-navmenu="Yemen"}
==============================================================================

Text analysis {data-navmenu="Yemen"}
==============================================================================

Stories {data-navmenu="Yemen"}
==============================================================================

Key Words in Context {data-navmenu="Yemen"}
==============================================================================


### Chart A

```{r}

```

### Chart B

```{r}

```

### Chart C

```{r}

```

